Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-14 Paper/ms.tex
Orbit writing

\section{Orbit Simulations}

The equations of motion were
\begin{eqnarray}
\ddot{x} &=& -\frac{x}{r^3} \\
\ddot{y} &=& -\frac{y}{r^3} \\
\end{eqnarray}
where $r = \sqrt{x^2 + y^2}$. The initial conditions
$\{x(0), y(0), \dot{x}(0), \dot{y}(0)\} = \{1, 0, 0, v\}$.

>>>>

\section{Orbit Simulations}
The expected (noise-free) signal due to an exoplanet is periodic, but
non-sinusoidal when the orbit is not perfectly circular. The expected
shape of the variations can be obtained from mechanical considerations.
To save time, we pre-computed the properties of orbits as a function of
ellipticity.

Consider a test particle moving in the $x$-$y$ plane under the influence of a
point mass at the origin. The equations of motion for the particle are:
\begin{eqnarray}
\frac{d^2x}{dt^2} &=& -\frac{x}{r^3} \\
\frac{d^2y}{dt^2} &=& -\frac{y}{r^3} \\
\end{eqnarray}
where $r = \sqrt{x^2 + y^2}$. The initial conditions
$\{x(0), y(0), \dot{x}(0), \dot{y}(0)\} = \{1, 0, 0, v\}$.
